### 2015-11-11 AssignmentV/Assignment5-Ditz_Schroeder-WS15-16.tex
Final_Benni_EX1
Hab das nohcmal durchgelesen und meiner meinung nahc angepasst an unser
besprochenes

Assume two sequences of length t with l mismatches. In the worst case, all mismatches are 
distributed uniformly. Than both sequences will share $l+1$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$.\\
\\
\noindent So both sequences share $l+1$ k-tuples of length $k = \lfloor\frac{t}{l+1}\rfloor$ and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.

>>>>

General we are now only looking at the worst case scenario, which means uniform distributed mistmatches in an alignment. Also we only look at $k>=1$, as $k=0$ is in our application not a useful result. Assume two sequences of length t with l mismatches.\\
 Than both sequences contain $l$ tuples of length $\lfloor\frac{t}{l+1}\rfloor$ and one tuple which has a length of maximal $\lfloor\frac{t}{l+1}\rfloor$ . Where $k = \lfloor\frac{t}{l+1}\rfloor$ is the maximal tuple length, possible in both sequences.\\
\\
\noindent So both sequences share $l+1$ k-tuples and for each 
$k \le \lfloor\frac{t}{l+1}\rfloor$ they share $(l+1) * \lfloor\frac{\lfloor\frac{t}{l+1}\rfloor}{k}\rfloor$
k-tuples.
